Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-03-01 Paper/Manuscript_Stats&Comp/reply_letter_STCO.tex
minor edits and comments

We would like to thank the reviewers for their thorough comments and valuable feedback. First, a summary with the improvements, changes and new insights achieved from the review are outlined. Then, all comments are addressed and there is a separate reply to each reviewer.

Authors would like the summary of the updates and insights presented above to be sent to all of the reviewers.

@@

@@

\item A brief discussion about the theoretical evidence of the near linear proportionality between the setting parameters of the model has been added (Section 4.2).

@@

@@

Reviewer \#1 comments "The authors correctly identify that for practical use in probabilistic programming environments the method has to be reliable and automatic enough, justifying the more detailed analysis of its parameters to identify when the approximation can be trusted. In addition, they provide the required implementations for one PP environment (Stan), although this is done at the level of case studies rather than integrating the approximation more tightly as part of a probabilistic programming environment."

@@

The diagnostic tool which consists in iterative steps to fit and diagnose the model has also been implemented in the \textit{brms} R-package. 
%This diagnostic iterative procedure is fundamentally based on a diagnostic rule to check whether the approximation is accurate and numerical equations allowing updating the key parameters of the method.

@@

Reviewer \#1 comments "The analysis is reasonable and provides tangible results on how the approximation scheme should be used, but does not go very deep. There are not new theoretical results but instead the analysis is purely empirical and in fact a standard study where each approximation parameter is varied at a time to identify the limits when the approximation starts to fail. The analysis is properly carried out and results in a practical diagnostic, but did not require notable scientific insight."

>>>>

We would like to thank the reviewers for their thorough comments and valuable feedback, which has helped us a lot in improving the paper. First, a summary of the improvements, changes, and new insights achieved during the revision are outlined. Then, all comments are addressed in a point-by-point manner, with separate replies to each reviewer. 
Throughout, comments or the reviewers are hightlighted in bold.

%Paul: all responses will be send to all reviewers anyway
%Authors would like the summary of the updates and insights presented above to be sent to all of the reviewers.

@@

%Paul: This list is way too long and detailed and appears to be redundant at times. I recommend focusing on between 4 and 7 or so points but more will be too much.

@@

\item A discussion about the theoretical evidence of the near linear proportionality between the setting parameters of the model has been added (Section 4.2).

@@

%Paul: Don't forget the thank the reviewers for their comments to show some more appreciation of their comments and time they put into the review.

@@

\textbf{The authors correctly identify that for practical use in probabilistic programming environments the method has to be reliable and automatic enough, justifying the more detailed analysis of its parameters to identify when the approximation can be trusted. In addition, they provide the required implementations for one PP environment (Stan), although this is done at the level of case studies rather than integrating the approximation more tightly as part of a probabilistic programming environment.}

@@

%Paul: The statement below is incorrect. I have not implemented the diagnostic procedure in brms.
%The diagnostic tool which consists in iterative steps to fit and diagnose the model has also been implemented in the \textit{brms} R-package. 
%This diagnostic iterative procedure is fundamentally based on a diagnostic rule to check whether the approximation is accurate and numerical equations allowing updating the key parameters of the method.

@@

%Paul: I recommend highlighting either the reviewers comments or our responses in bold to clearly differentiate what the reviewers wrote and what we wrote. Example below.

\textbf{The analysis is reasonable and provides tangible results on how the approximation scheme should be used, but does not go very deep. There are not new theoretical results but instead the analysis is purely empirical and in fact a standard study where each approximation parameter is varied at a time to identify the limits when the approximation starts to fail. The analysis is properly carried out and results in a practical diagnostic, but did not require notable scientific insight.}
